Geometric variational problems

### 2020-11-16 NSF2020/Description/newspecificaim3.tex
edited rest of proposal

\subsubsection{Vesicles in background flows}
Numerically solving the Stokes and screened Laplace system~\eqref{SL}
and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
robust, high-order-in-time and -space algorithms suited to the problem.
There are a few challenges. {\bf (1)} The equations express a two-way coupling
since the flow changes the position of the suspended particles,
and in return, the geometry-dependent hydrophobic stresses impart a force
on the flow. {\bf (2)} The inputs to the Stokes equations are particle
configurations, forces, and torques. The outputs are the rigid body
translation and angular velocities used to update the particle positions
(see Figure~\ref{fig:flow_map}). Although the underlying equations are
linear, the overall problem is highly nonlinear because the domain is
constantly changing. {\bf (3)} Self-assembly causes the particles to
come into close contact. As a result, an exceptional spatial accuracy is
required to resolve the fields between adjacent particles. Furthermore, 
physically relevant elastic properties of bilayers become apparent at
large length scales and for large particle-numbers, which increases the
computational complexity of our simulations.

We include a background flow by replacing the third equation in
\eqref{eq:stokes} with the condition $\mathbf{u}(\mathbf{x})
\to \mathbf{u}_{\infty}(\mathbf{x})$ as $|\mathbf{x}| \to
\infty$. To incorporate the far-field flow, we use the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + L\boldsymbol{\eta} + 
    \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i\right),
\end{align}
where $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers~\cite{leal_2007} and $L\boldsymbol{\eta}$ is a layer
potential for the unknown density function $\boldsymbol{\eta}$. With the
exception of the rigid body conditions, the
representation~\eqref{PowerMiranda} automatically satisfies all the
hydrodynamic equations including the far-field condition. The rigid
body conditions follow by requiring the viscous stresses to vanish across
the particle boundaries.
%
We will compare the behavior of our particle-based vesicles in Stokes
flow to well-established models that enforce area incompressibility and
volume conservation in vesicle membrane
dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
\S \ref{sec:preliminary_work} contains our preliminary results.
%
%Our
%preliminary results show that the particle-based bilayers have the same
%large area modulus as real lipid bilayer membranes, so we expect
%realistic results from our flow simulations. Under moderate shear rates,
%the vesicle elongates and takes on the tank-treading elliptical shape.
%We can directly check for area compressibility and volume conservation
%properties from particle simulations by tracking the change in area
%density of the midplane as a function of shear flow rate, along with
%evaluating the tangential divergence of the velocity.
%
%Bilayer membranes have a small permeability to
%water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
%a vesicle membrane that conserves volume. In our particle-based
%approach, water motion across the bilayer is limited by the size of the
%gaps between the particles, which is an artifact of coarse-graining.
%Making these gaps smaller comes at the expense of numerical accuracy,
%and we will assess if there is a reasonable trade-off between
%approximate volume conservation and simulation complexity. 
%
%Finally, the particle-based vesicle bilayers have two distinct leaflets
%consisting of the particles in contact with the vesicle interior, and
%those in contact with the surrounding fluid. Since there is a nonzero
%separation between these layers, an important effect we observe is that
%the leaflets slide against one another under shear flow. This implies
%that part of the viscous dissipation in the aqueous phase is enhanced by
%intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
%Intermonolayer slip enters zero-thickness membrane models as a velocity
%jump boundary condition and leads to multiple solution
%states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
%intermonolayer slip is an artifact of monolayer independence and we can
%control for slip as a function of shear rate, vesicle diameter, and
%particle geometry.

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending rigidity
was determined as a function of lipid composition from 0 to 100 mol $\%$ of
charged lipids using flicker spectroscopy of the shape fluctuations of a giant
unilamellar vesicle (GUV).
%the bending rigidity is determined as a
%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
Membrane bending rigidity increases with increasing lipid surface charge,
while decreases with increasing salt concentration in the bulk solution
due to the screening of the lipid surface charge. This
agrees with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would worsen in the presence of
electrostatic interactions and electrokinetics. The PIs will extend
the approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic forces to the hydrophobic attraction forces
between particles to compute the particle assembly dynamics, we can then
calculate elastic moduli as outlined in \S\ref{subsec:specific_aim_1}.
Results from these proposed calculations will provide further comparisons and
validations of the HAP model against the continuum mechanics.

>>>>

\subsubsection{Vesicles in background flows}
Numerically solving the Stokes and screened Laplace system~\eqref{SL}
and~\eqref{eq:stokes} is nontrivial, and we will develop efficient,
robust, high-order-in-time and -space algorithms suited to the problem.
There are a few challenges. {\bf (i)} The equations express a two-way
coupling since the flow changes the position of the suspended particles,
and in return, the geometry-dependent hydrophobic stresses impart a
force on the flow. {\bf (ii)} The inputs to the Stokes equations are
particle configurations, forces, and torques. The outputs are the rigid
body translation and angular velocities used to update the particle
positions (see Figure~\ref{fig:flow_map}). Although the underlying
equations are linear, the overall problem is highly nonlinear because
the domain is constantly changing. {\bf (iii)} Self-assembly causes the
particles to come into close contact. As a result, an exceptional
spatial accuracy is required to resolve the fields between adjacent
particles. Furthermore, physically relevant elastic properties of
bilayers become apparent at large length scales and for large
particle-numbers, which increases the computational complexity of our
simulations.

We include a background flow by replacing the third equation in
\eqref{eq:stokes} with the condition $\mathbf{u}(\mathbf{x})
\to \mathbf{u}_{\infty}(\mathbf{x})$ as $|\mathbf{x}| \to
\infty$. To incorporate the far-field flow, we use the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + \mathcal{K}\boldsymbol{\eta} + 
    \sum_{i=1}^N \left(S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i\right),
\end{align}
where $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers~\cite{leal_2007} and $\mathcal{K}\boldsymbol{\eta}$ is a layer
potential for the unknown density function $\boldsymbol{\eta}$. With the
exception of the rigid body conditions, the
representation~\eqref{PowerMiranda} automatically satisfies all the
hydrodynamic equations including the far-field condition. The rigid
body conditions follow by requiring the viscous stresses to vanish across
the particle boundaries.
%
We will compare the behavior of our particle-based vesicles in Stokes
flow to well-established models that enforce area incompressibility and
volume conservation in vesicle membrane
dynamics~\cite{torres-sanchez_millan_arroyo_2019,mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}.
\S \ref{sec:preliminary_work} contains our preliminary results.
%
%Our
%preliminary results show that the particle-based bilayers have the same
%large area modulus as real lipid bilayer membranes, so we expect
%realistic results from our flow simulations. Under moderate shear rates,
%the vesicle elongates and takes on the tank-treading elliptical shape.
%We can directly check for area compressibility and volume conservation
%properties from particle simulations by tracking the change in area
%density of the midplane as a function of shear flow rate, along with
%evaluating the tangential divergence of the velocity.
%
%Bilayer membranes have a small permeability to
%water~\cite{323e9a2f0c58487ea82518d7a1f96485}, and modelers often assume
%a vesicle membrane that conserves volume. In our particle-based
%approach, water motion across the bilayer is limited by the size of the
%gaps between the particles, which is an artifact of coarse-graining.
%Making these gaps smaller comes at the expense of numerical accuracy,
%and we will assess if there is a reasonable trade-off between
%approximate volume conservation and simulation complexity. 
%
%Finally, the particle-based vesicle bilayers have two distinct leaflets
%consisting of the particles in contact with the vesicle interior, and
%those in contact with the surrounding fluid. Since there is a nonzero
%separation between these layers, an important effect we observe is that
%the leaflets slide against one another under shear flow. This implies
%that part of the viscous dissipation in the aqueous phase is enhanced by
%intermonolayer friction~\cite{SHKULIPA2005823, ShkulipaThesis}.
%Intermonolayer slip enters zero-thickness membrane models as a velocity
%jump boundary condition and leads to multiple solution
%states~\cite{schwalbe_vlahovska_miksis_2010}. In the present proposal,
%intermonolayer slip is an artifact of monolayer independence and we can
%control for slip as a function of shear rate, vesicle diameter, and
%particle geometry.

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending
rigidity was determined as a function of lipid composition from 0 to 100
mol $\%$ of charged lipids using flicker spectroscopy of the shape
fluctuations of a giant unilamellar vesicle (GUV).
%the bending rigidity is determined as a
%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
Membrane bending rigidity increases with increasing lipid surface
charge, while decreases with increasing salt concentration in the bulk
solution due to the screening of the lipid surface charge. This agrees
with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would worsen in the presence of
electrostatic interactions and electrokinetics. The PIs will extend the
approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic force to the hydrophobic attraction force
between particles, we will assess the dependence of elastic moduli on
electric charges using the methods described in
\S\ref{subsec:specific_aim_1}. Results from these proposed calculations
will provide further comparisons and validations of the HAP model
against the continuum mechanics.

### 2020-11-16 NSF2020/Description/preliminarywork.tex
edited rest of proposal

\vspace{-0.1cm}
\begin{wraptable}[8]{r}{0.55\textwidth}
\vspace{-0.1cm}
\centering{
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP                     & experiment          & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
}
  \vspace{-8pt}
\caption{\label{tab:moduli} \footnotesize Comparison of values of elastic
  moduli from the experimental literature and derived by HAP
  simulation.} 
\end{wraptable}
\section{Preliminary work}
\label{sec:preliminary_work}
PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
%
%
%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
%PhD student and is currently a postdoc with PI RR. The collaboration
%involved theoretical work and simulation. The theoretical work included
%model development, proving the first variation formula~\eqref{stress}
%and force-free law, and an energy-based uniqueness theorem for the
%exterior domain problem~\eqref{SL}. 
%Coauthors Andreas Kl\"ockner
%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
%simulations on NJIT clusters.
%
%\begin{wraptable}[11]{l}{0.43\textwidth}
%\centering{
%  \begin{tabular}{|l|l|l|l|}
%    $n$   & (rel.~err.)$_F$
%    &  (rel.~err.)$_G$ \\
%    \hline
%% 32   &   4.07466     &   1.56437\\
%% 64   &   0.24664     &   0.03476\\
%% 128  &   0.00063     &   0.00006\\
%  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
%  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
%  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
%  \end{tabular}}
%\vspace{-5pt}
%\caption{\label{tab:spectral_force} 
%\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
%  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
%  and (rel.~err.)$_G = \max_{i}
%  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
%  for force and torque respectively as a function of number of grid
%  points $n$ per particle.  The data is for $N = 5$ particles; two of
%  the particles are nearly touching at a distance 1\% of particle
%  diameter.} 
%\end{wraptable}
The results are summarized in \cite{Fu2018_SIAM}, where
small particle-number simulations successfully demonstrated gradient-driven self-assembly of
amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
the model parameters: decay length $\rho=2.5$ nm (based on measurements of
hydrophobic attraction between surfactant-coated
surfaces~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
particle diameter $\delta = 2.0$ nm (the physical monolayer thickness~\cite{Boal}),
and interfacial tension $\gamma = 4$ pN nm$^{-1}$ (based on
measurements for single-component bilayer lipid
membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}).

%\begin{wrapfigure}[]{r}{0.5\textwidth}
%  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
%  \vspace{-25pt}
%  \caption{\label{fig:tank_treading} \footnotesize
%    Panel A shows water activity and flow direction for  a two-dimensional
%    particle-based vesicle in a shear flow; $\mu  = 1$ mPa s,
%    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. Panel B plots the
%    mean angular velocities for the outer leaflet and the inner
%    respectively.  Panel C shows that the trajectory of the particle
%    centers forms two ellipses with well-defined inclination angle
%    $\Theta$. Panel D shows the evolution of the inclination angle.
%    Panels B and D share the same time axis.}
%\end{wrapfigure}
\begin{wraptable}[10]{l}{0.43\textwidth}
\centering{
  \begin{tabular}{|l|l|l|l|}
    $n$   & (rel.~err.)$_F$
    &  (rel.~err.)$_G$ \\
    \hline
% 32   &   4.07466     &   1.56437\\
% 64   &   0.24664     &   0.03476\\
% 128  &   0.00063     &   0.00006\\
  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
  \end{tabular}}
\vspace{-5pt}
\caption{\label{tab:spectral_force} 
\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
  and (rel.~err.)$_G = \max_{i}
  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
  for force and torque, respectively, as a function of number of grid
  points $n$ per particle. The data is for $N = 5$ particles; two of
  the particles are nearly touching at a distance 1\% of particle
  diameter.} 
\end{wraptable}
The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
loading a partially clamped planar bilayer. The second used a harmonic
bond to dilate a circular bilayer. The third measured tilt using a decay
equation from~\cite{KUZMIN2005}. These simulations isolated three of the
five deformations of~\eqref{ansatz3}, enabling us to read off elastic
moduli from simulation data. The results agreed remarkably well with the
values reported in the experimental literature (Table~\ref{tab:moduli}).
The agreement is underscored by the fact that the two main HAP
parameters, $\gamma$ and $\rho$, were assigned physical values from the
outset rather than being tuned to fit data.

PIs BQ, RR, and YNY initiated a collaboration in summer 2020 to
develop the hydrodynamic model of \S\ref{subsec:specific_aim_3}.  To
date, we have written solvers for the two-dimensional boundary integral
formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
third-order accuracy up to the boundary. The specialized reciprocal
identity~\eqref{eq:reciprocal} gives spectral accuracy for force and
torque (Table~\ref{tab:spectral_force}).

\begin{wrapfigure}[22]{r}{0.5\textwidth}
\vspace{-5pt}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional, 
    particle-based vesicle in a shear flow (arrows); $\mu  = 1$ mPa s and
    $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$. (Compare with \cite{Brandner2019}).
    Panel B: Angular velocities for the outer and the inner leaflets.
    Panel C: The trajectory of the particle
    centers forms two ellipses with well-defined inclination angle
    $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}
We have simulated two-dimensional vesicles in shear flow
$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
$\dot{\gamma}$,
%(The symbol shear rate is unrelated to interfacial tension.)
and the particle-based system mimics the behavior observed in continuous
vesicles~\cite{torres-sanchez_millan_arroyo_2019,
mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
pattern is that of a vesicle bilayer approaching a steady, tank-treading
ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
data in the context of theoretical work on
tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
a tank-treading frequency as the mean of the particle angular
velocities. The measured steady-state frequencies were within 7\% of the predicted 
frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
The inclincation angle of the particle-based simulation also
follows the inclination angle $\Theta(t)$ predicted by Jeffrey's
equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation
coming from particle reorganization.

@@

\begin{wrapfigure}[10]{l}{0.22\textwidth}
% \vspace{-5pt}
  \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
 \vspace{-20pt}
  \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
  two-dimensional vesicle at large shear rates.}
\end{wrapfigure}
The above considerations further justify using the particle-based model
to study material properties as outlined in
\S\ref{subsec:specific_aim_1}. Furthermore, the particle system allows
for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}. In
Figure \ref{fig:tank_treading}B, the inner angular velocity is slightly
less than the outer angular velocity. Intermonolayer slip enters
zero-thickness membrane models as a velocity jump boundary condition
\cite{schwalbe_vlahovska_miksis_2010}, for example, but in the present
model, it is a consequence of monolayer independence. For large shear
rates, viscous forces exceed the hydrophobic attraction leading to
 vesicle rupture~\cite{C8SM01501E}, at which point the flow carries away segmented membrane patches
(Figure \ref{fig:flow_rupture}).

>>>>

\begin{wraptable}[6]{r}{0.55\textwidth}
\vspace{-0.8cm}
\centering{
  \begin{tabular}{|l|r|r|p{0.1\textwidth}|}
    \hline
          & HAP                     & experiment          & ref.\\
    \hline 
    $\KB$ & $11 \pm 2.5$ \kBT       & 10 \kBT               & \cite{Naetal15,VeBrPa15,NAGLE2000159,PhysRevLett.113.248102}\\
    \hline 
    $\KA$ & $34$ \kBT \; nm$^{-2}$  & 30--40 \kBT nm$^{-2}$ & \cite{Nagle17, Nagle17-2}\\
    \hline 
    $\KTH$ & $12$ \kBT \; nm$^{-2}$ & 10 \kBT nm$^{-2}$     & \cite{KUZMIN2005, KoNa15} \\ \hline
  \end{tabular}
}
  \vspace{-8pt}
\caption{\label{tab:moduli} \footnotesize Comparison of values of elastic
  moduli from the experimental literature and derived by HAP
  simulation.} 
\end{wraptable}
\section{Preliminary work}
\label{sec:preliminary_work}
PIs RR and YNY started work on HAP modeling with Szu-Pei Fu (then PI YNY's student and now PI RR's postdoc) and collaborators in 2017. 
%
%
%The HAP project was initiated in 2017 by PI RR and YNY. The lead author
%on our first paper~\cite{Fu2018_SIAM} was Szu-Pei Fu, who was PI YNY's
%PhD student and is currently a postdoc with PI RR. The collaboration
%involved theoretical work and simulation. The theoretical work included
%model development, proving the first variation formula~\eqref{stress}
%and force-free law, and an energy-based uniqueness theorem for the
%exterior domain problem~\eqref{SL}. 
%Coauthors Andreas Kl\"ockner
%(Computer Science, UIUC, NSF CAREER \#1654756) and his PhD student Matt
%Wala provided their Quadrature by Expansion, or QBX algorithm and Fu ran
%simulations on NJIT clusters.
%
%\begin{wraptable}[11]{l}{0.43\textwidth}
%\centering{
%  \begin{tabular}{|l|l|l|l|}
%    $n$   & (rel.~err.)$_F$
%    &  (rel.~err.)$_G$ \\
%    \hline
%% 32   &   4.07466     &   1.56437\\
%% 64   &   0.24664     &   0.03476\\
%% 128  &   0.00063     &   0.00006\\
%  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
%  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
%  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
%  \end{tabular}}
%\vspace{-5pt}
%\caption{\label{tab:spectral_force} 
%\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
%  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
%  and (rel.~err.)$_G = \max_{i}
%  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
%  for force and torque respectively as a function of number of grid
%  points $n$ per particle.  The data is for $N = 5$ particles; two of
%  the particles are nearly touching at a distance 1\% of particle
%  diameter.} 
%\end{wraptable}
The results are summarized in \cite{Fu2018_SIAM}, where
small particle-number simulations successfully demonstrated gradient-driven self-assembly of
amphiphilic particles into two-dimensional micelles and bilayer membranes with realistic values of
the model parameters: decay length $\rho=2.5$ nm (based on measurements of
hydrophobic attraction between surfactant-coated
surfaces~\cite{Eriksson1989, Lin2005, Parsegian, Israelachvili80}),
particle diameter $\delta = 2.0$ nm (the physical monolayer thickness~\cite{Boal}),
and interfacial tension $\gamma = 4$ pN nm$^{-1}$ (based on
measurements for single-component bilayer lipid
membranes~\cite{GarciaSaez, KUZMIN2005, Petelska2012, Jackson2016}).

\begin{wraptable}[10]{l}{0.43\textwidth}
  \vspace{-6pt}
\centering{
  \begin{tabular}{|l|l|l|l|}
    $n$   & (rel.~err.)$_F$
    &  (rel.~err.)$_G$ \\
    \hline
% 32   &   4.07466     &   1.56437\\
% 64   &   0.24664     &   0.03476\\
% 128  &   0.00063     &   0.00006\\
  32  & $4.07 \times 10^{+0}$ & $1.56 \times 10^{+0}$ \\
  64  & $2.47 \times 10^{-1}$ & $3.48 \times 10^{-2}$ \\
  128 & $6.30 \times 10^{-4}$ & $6.00 \times 10^{-5}$ 
  \end{tabular}}
\vspace{-8pt}
\caption{\label{tab:spectral_force} 
\footnotesize  Relative numerical errors (rel.~err.)$_F = \max_{i}
  \|\mathbf{F}_i-\mathbf{F}_i^{\text{exact}}\|/\|\mathbf{F}_i^{\text{exact}}\|$
  and (rel.~err.)$_G = \max_{i}
  \|\mathbf{G}_i-\mathbf{G}_i^{\text{exact}}\|/\|\mathbf{G}_i^{\text{exact}}\|$
  for force and torque, respectively, as a function of number of grid
  points $n$ per particle. The data is for $N = 5$ particles; two of the
  particles are nearly touching at a distance of 1\% of the particle
  diameter.} 
\end{wraptable}
The paper \cite{Fu2018_SIAM} considered three types of simulations. The first measured bending by
loading a partially clamped planar bilayer. The second used a harmonic
bond to dilate a circular bilayer. The third measured tilt using a decay
equation from~\cite{KUZMIN2005}. These simulations isolated three of the
five deformations of~\eqref{ansatz3}, enabling us to read off elastic
moduli from simulation data. The results agreed remarkably well with the
values reported in the experimental literature (Table~\ref{tab:moduli}).
The agreement is underscored by the fact that the two main HAP
parameters, $\gamma$ and $\rho$, were assigned physical values from the
outset rather than being tuned to fit data.

PIs RR, BQ, and YNY initiated a collaboration in summer 2020 to develop
the hydrodynamic model of \S\ref{subsec:specific_aim_3}. To date, we
have written solvers for the two-dimensional boundary integral
formulations of~\eqref{SL} and~\eqref{eq:stokes} that achieve
third-order accuracy up to the boundary of the particles. The
specialized reciprocal identity~\eqref{eq:reciprocal} gives spectral
accuracy for force and torque (Table~\ref{tab:spectral_force}).

\begin{wrapfigure}[22]{r}{0.5\textwidth}
\vspace{-5pt}
  \centering{\includegraphics[width=0.5\textwidth]{Figures/TankTreading.pdf}}
  \vspace{-25pt}
  \caption{\label{fig:tank_treading} \footnotesize
    Panel A: A two-dimensional, particle-based vesicle in a shear flow
    (arrows); $\mu = 1$ mPa s and $\dot{\gamma} = 0.5$ $\mu$s$^{-1}$
    Compare with~\cite{Brandner2019}).  Panel B: Angular velocities for
    the outer and the inner leaflets.  Panel C: The trajectory of the
    particle centers forms two ellipses with well-defined inclination
    angle $\Theta$. Panel D: The evolution of the inclination angle.
    Panels B and D share the same time axis.}
\end{wrapfigure}
We have simulated two-dimensional vesicles in shear flow
$\mathbf{u}_{\infty} = \dot{\gamma} x_2 \mathbf{i}_1$ with shear rate
$\dot{\gamma}$,
%(The symbol shear rate is unrelated to interfacial tension.)
and the particle-based system mimics the behavior observed in continuous
vesicles~\cite{torres-sanchez_millan_arroyo_2019,
mahapatra_saintillan_rangamani_2020, Steigmann99, C6SM02452A}. The basic
pattern is that of a vesicle bilayer approaching a steady, tank-treading
ellipse (Figure~\ref{fig:tank_treading}C). We analyzed the simulation
data in the context of theoretical work on
tank-treading~\cite{Finken2008, PhysRevLett.106.158103}.
Jeffrey's equation predicts a tank-treading frequency $-\dot{\gamma}/2$ (dashed line in
Figure~\ref{fig:tank_treading}B). In the particle simulation, we measured
a tank-treading frequency as the mean of the particle angular
velocities. The measured steady-state frequencies were within 7\% of the predicted 
frequency (dotted and solid curves in Figure~\ref{fig:tank_treading}B).
The inclincation angle of the particle-based simulation also
follows the inclination angle $\Theta(t)$ predicted by Jeffrey's
equation (Figure~\ref{fig:tank_treading}D), albeit with higher frequency oscillation
coming from particle reorganization.

@@

\begin{wrapfigure}[10]{l}{0.22\textwidth}
 \vspace{-3pt}
  \centering{\includegraphics[width=0.22\textwidth]{Figures/PW_fig5.pdf}}
 \vspace{-20pt}
  \caption{\label{fig:flow_rupture} \footnotesize Rupture of a
  two-dimensional vesicle at large shear rates.}
\end{wrapfigure}
The above considerations further justify using the particle-based model
to study material properties as outlined in
\S\ref{subsec:specific_aim_1}. Furthermore, the particle system allows
for intermonolayer slip~\cite{SHKULIPA2005823, ShkulipaThesis}. In
Figure \ref{fig:tank_treading}B, the inner angular velocity is slightly
less than the outer angular velocity. Intermonolayer slip enters
zero-thickness membrane models as a velocity jump boundary condition
\cite{schwalbe_vlahovska_miksis_2010}, for example, but in the present
model, it is a consequence of monolayer independence. For large shear
rates, viscous forces exceed the hydrophobic attraction leading to
 vesicle rupture~\cite{C8SM01501E}, at which point the flow carries away segmented membrane patches
(Figure \ref{fig:flow_rupture}).
